---
title: "bayesTFR - Third Try"
author: "Giulia Gonnella"
date: "5/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 0. See if this works

## 1. Introduction
The scope of this script is to investigate the use of R package *bayesTFR*, which uses a Bayesian Hierarchical model to produce probabilistic projections of annual TFR accounting for the uncertainty in the past values.

## 2. Input
### 2.1 Packages
Upload all the useful R packages and related ones. 
```{r, results = 'hide', message = FALSE, warning = FALSE}
.packages = c("countrycode", "cwhmisc", "data.table", "data.table", "plyr", 
              "dplyr", "devtools", "bayesTFR", "ggplot2", "googleVis", "httr", "knitr", 
              "kableExtra", "lubridate", "memisc", "openxlsx", "readxl", "rje",  
              "rlang", "RODBC", "rworldmap", "signal", "stringdist", "stringi", 
              "stringr", "tm", "vctrs", "tidyverse", "xlsx", "XML")


.inst <- .packages %in% installed.packages()

if(length(.packages[!.inst]) > 0) 
  install.packages(.packages[!.inst],dependencies=TRUE)

lapply(.packages, require, character.only=TRUE)

getwd()
```


## 3. 5-year version
## 3.1 Output directory
```{r}
simulation.dir <- file.path(getwd(), "New")
```

### 3.2 Phase II
#### 3.2.1 Fitting the TFR projection model
Run MCMC for simulating TFR for all countries (as they all are in Phase II - during the fertility transition), using a Bayesian hierarchical model. 
```{r}
m1 <- run.tfr.mcmc(nr.chains = 5,
                   iter = 5000,
                   output.dir = simulation.dir,
                   replace.output = T)

#Access the MCMC results
m2 <- get.tfr.mcmc(sim.dir = simulation.dir)

summary(m2)
summary(m2, meta.only = T) 

tfr.pardensity.plot(m2,
                    par.names = c("alphat",
                                  "Triangle4",
                                  "delta",
                                  "sigma0"),
                    dev.ncol = 4,
                    bw = 0.5)

tfr.partraces.plot(mcmc.list = m2,
                   par.names = "Triangle4",
                   nr.points = 100)



```

#### 3.2.2 View estimation results
```{r}
#Country-independent parameters
tfr.parameter.names()

tfr.partraces.plot(m2,
                   par.names = c("chi", "psi", 
                                 "Triangle4", "const_sd"),
                   dev.ncol = 2)

tfr.partraces.plot(m2,
                   par.names = c("delta", "delta4"),
                   dev.ncol = 2)

tfr.partraces.plot(m2,
                   par.names = c("alpha", "alphat"),
                   dev.ncol = 3)

tfr.partraces.plot(m2,
                   par.names = c("a_sd", "b_sd", 
                                 "S_sd", "sigma0", 
                                 "mean_eps_tau", "sd_eps_tau"),
                   dev.ncol = 3)

#Country-specific parameters
summary(m2, country = "Thailand")

tfr.parameter.names.cs()

tfr.partraces.cs.plot(m2, 
                      country = "Thailand")

#Posterior density
tfr.partraces.cs.plot(m2, 
                      country = "Thailand")

tfr.pardensity.cs.plot(m2, 
                       country = "Thailand", 
                       burnin = 30)

tfr.pardensity.cs.plot(m2, 
                       country = "Thailand", 
                       burnin = 200, 
                       par.names = "Triangle_c4")

#Double logistic curve
DLcurve.plot(m2, 
             country = "Thailand", 
             burnin=100, 
             nr.curves=100)
```

#### 3.2.3 MCMC convergence diagnostic 
```{r}
diag1 <- tfr.diagnose(simulation.dir,
                      thin = 10,
                      burnin = 500)

diag2 <- get.tfr.convergence(simulation.dir,
                             thin = 10,
                             burnin = 500)
summary(diag2)
```


### 3.3 Phase III
#### 3.3.1 Run Phase III MCMC
```{r}
install.packages("shinystan", dependencies=TRUE)
library(shinystan)

m_PhaseIII <- run.tfr3.mcmc(sim.dir = simulation.dir, 
                            iter= 10000, 
                            thin = 10,
                            nr.chains=5,
                            replace.output = T)

m3 <- get.tfr3.mcmc(simulation.dir)

summary(m3, meta.only = T)

get.countries.table(m3)

```

#### 3.3.2 View estimation results
```{r}
#Country-independent parameters
tfr3.parameter.names()

tfr3.partraces.plot(m3,
                   dev.ncol = 3)

#Country-specific parameters
Country = "Italy"

summary(m3, 
        country = Country)

tfr3.parameter.names.cs()

tfr3.partraces.cs.plot(m3, 
                      country = Country)

#Posterior density
tfr3.pardensity.cs.plot(m3, 
                       country = Country, 
                       burnin = 2000)
```

#### 3.3.3 MCMC convergence diagnostic
```{r}
diag3 <- tfr3.diagnose(simulation.dir, 
                       burnin = 10)

diag3 <- get.tfr3.convergence(simulation.dir,
                      thin = 10,
                      burnin = 2000)
```


### 3.4 Projections
#### 3.4.1 Generating projections
Generate the TFR trajectories.
```{r}
pred1 <- tfr.predict(sim.dir = simulation.dir, 
                     end.year = 2100,
                     replace.output = T,
                     burnin = 2000,
                     nr.traj = 4000,
                     use.tfr3 = T,
                     burnin3 = 2000,
                     verbose = T)

pred1 <- get.tfr.prediction(sim.dir = simulation.dir)

```

#### 3.4.2 View projections results
```{r}
Country <- 840

summary(pred1, 
        country = Country)

tfr.trajectories.table(pred1, 
                       country = Country, 
                       pi = c(80, 90))

tfr.trajectories.plot(pred1, 
                      country = Country, 
                      nr.traj = 100)

tfr.trajectories.plot(pred1, 
                      country = Country, 
                      typical.trajectory=TRUE)

tfr.trajectories.plot(pred1, 
                      country = Country, 
                      nr.traj = 100,
                      mark.estimation.points = TRUE)

tfr.map(pred1)


```


## 4. Annual version
### 4.1 Output directory
```{r}
simulation_annual.dir <- file.path(getwd(), "Annual")
```

### 4.2 Fitting the TFR projection model
Run MCMC for simulating TFR for all countries (as they all are in Phase II - during the fertility transition), using a Bayesian hierarchical model. 
```{r}
m1_annual <- run.tfr.mcmc(nr.chains = 5,
                          iter = 20000,
                          output.dir = simulation_annual.dir,
                          replace.output = T, 
                          annual = T)

#Access the MCMC results
m2_annual <- get.tfr.mcmc(sim.dir = simulation_annual.dir)

summary(m2_annual)
summary(m2_annual, meta.only = T) 

tfr.pardensity.plot(m2_annual,
                    par.names = c("alphat",
                                  "Triangle4",
                                  "delta",
                                  "sigma0"),
                    dev.ncol = 4,
                    bw = 0.5)
```


### 4.3 MCMC convergence diagnostic
```{r}
diag1_annual <- tfr.diagnose(simulation_annual.dir,
                             thin = 10,
                             burnin = 2000)

diag2_annual <- get.tfr.convergence(simulation_annual.dir,
                                    thin = 10,
                                    burnin = 2000)

summary(diag2_annual)
```

### 4.4 Run Phase III MCMC
```{r}
install.packages("shinystan", dependencies=TRUE)
library(shinystan)

m_PhaseIII_annual <- run.tfr3.mcmc(sim.dir = simulation_annual.dir, 
                            iter= 100000,
                            nr.chains=5,
                            replace.output = T,
                            annual = T)

m3_annual <- get.tfr3.mcmc(simulation_annual.dir)

summary(m3_annual)

diag3_annual <- tfr3.diagnose(simulation_annual.dir, 
                       burnin = 2000)

diag3_annual <- get.tfr3.convergence(simulation_annual.dir,
                      thin = 10,
                      burnin = 2000)
```






